Reliable error estimation for Sobol' indices\thanks{This work is supported by the CITiES project funded by the Agence Nationale de la Recherche (grant ANR-12-MONU-0020) and by the United States National Science Foundation (grant DMS-1522687).}

### 2017-02-14 article_review/reviewer_letter.tex
modifs in reviewer's letter

{\color{blue} Thank you for this remark. The definition was intended to include only point sets where all points are coordinate-wise different. Namely, consider a point set $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and two points $\vx_{i_1}$, $\vx_{i_2}$, $i_1 \neq i_2$. Then $\vx_{i_1}$ and $\vx_{i_2}$ are coordinate-wise different if: 
$$ x_{i_1,j} \neq x_{i_2,j}, \qquad \forall j=1,\dots,d .$$
Definition 1 has been reworked to include this property. This also tackles the issue of having more than one permutation that would rearranges the rows $\vx'_i$ into $\vx_i$. Now, the permutation is unique.

Furthermore, a remark was added to specify that in this paper $\mathcal{P}$ and $\mathcal{P}'$ are constructed to avoid the degenerate case $\forall i, \ \vx'_i=\vx_i$.}

@@

@@

@@

\item[8.] Sobol' indices are often motivated by the need to identify important variables when $f$ is expensive to evaluate; perhaps half a day for $n = 1$. Estimates that require $n$ to be several hundred thousand do not fitthat motivating context. If the authors can describe a context where it would be worth having $n = 400000$ to get a Sobol' estimate, that would be great. Nobody else has properly addressed this issue, so this point is a
suggestion, not a requirement.
\end{itemize}

@@

\item[f.] page $8$ line $16$: twice as small  $\rightarrow$ half as large
\end{itemize}
\end{document}

>>>>

{\color{blue} We thank the reviewer for this remark. The definition was intended for point sets where all points are coordinate-wise different. More precisely, consider a point set $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and two points $\vx_{i_1}$, $\vx_{i_2}$, $i_1 \neq i_2$. Then $\vx_{i_1}$ and $\vx_{i_2}$ are coordinate-wise different if: 
$$ x_{i_1,j} \neq x_{i_2,j}, \qquad \forall j=1,\dots,d .$$
Definition 1 has been reworked to include this property. This also tackles the issue of having more than one permutation that would rearrange the rows $\vx'_i$ into $\vx_i$. Now, the permutation is unique.

Furthermore, a remark was added to specify that in this paper $\mathcal{P}$ and $\mathcal{P}'$ are constructed to avoid the degenerate case: $\forall i, \ \vx'_i=\vx_i$.}

@@

{\color {blue} We acknowledge that Sobol' indices are theoretically invariant by adding a constant shift $c$ to the studied function. As underlined by the reviewer, the addition of a constant shift $c$ modifies the error bound for $\vI_3$ but also the errors bounds for the others integrands ($\vI_1$, $\vI_2$ and $\vI_4$). More generally, our algorithm depends on the analytical expression of the Sobol' index estimator considered.

However, that is not a concerns since error bounds for any estimator can be calculated. That is, our algorithm can be adapted to any Sobol' index estimator. In particular, this is done when ``Correlation 2'' is used in Variant A.b instead of (5).}

@@

{\color{blue} The Sobol' g-function has been modified according to the reviewer remark. Corresponding tables and figures have changed.}

@@

{\color{blue} The Asian option problem has been replaced by the wing weight test function taken from the suggested database. Section $5.2$ has been reworked to introduce this new test function. Our results are compared to formers obtained by screening approaches.}

\item[8.] Sobol' indices are often motivated by the need to identify important variables when $f$ is expensive to evaluate; perhaps half a day for $n = 1$. Estimates that require $n$ to be several hundred thousand do not fitthat motivating context. If the authors can describe a context where it would be worth having $n = 400000$ to get a Sobol' estimate, that would be great. Nobody else has properly addressed this issue, so this point is a
suggestion, not a requirement.

{\color{blue} We understand and agree with the issue raised by the reviewer. A possible solution is to choose a higher target precision $\epsilon$ when dealing with time-expensive function. In the proposed examples, $\epsilon$ was intentionally fixed small to put forward the performance of our algorithm. To cover both situations (small and high value of $\epsilon$), the bratley example has been reworked.

On another hand, if one has to deal with a function where one day is required to obtain one evaluation, perhaps the use of Sobol' indices should be dropped for a screening method (less accurate but less greedy). Or if available, one could make use of a cluster to perform multiple model evaluations in parallel.}
\end{itemize}

@@

\item[f.] page $8$ line $16$: twice as small  $\rightarrow$ half as large
\end{itemize}

{\color{blue} All minors points have been dealt with. For point c., equation (7) was replaced with the unbiased estimator of $\sigma^2$. For point e., the distinction has been noted in the paper given that notations cannot be changed (they need to match those of the sourced paper).
\end{document}
